The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-05-08 intro.tex
要开始写生态模型了，准备会议以及POMS
去除子文件的其他导言
初步
struct done
init on mac
start the schedule and evolve modules.
增加文章结构

% !Mode:: "TeX:UTF-8"
% !TEX root = Eco-Model.tex
\section{test}

>>>>

% !TEX root = Eco-Model.tex
\section{Introduction}
First of all, just say something about the cloud mfg shortly,
then, tell something about the aim or the meaning of the research,
and how is the recent research work, what's new of your work

The intro should cover 
\begin{itemize}
	\item Theme or Topic (keep it simple, do not begin with research question or hypothesis. Define technical terms and constructs concepts.)
	\item Academic Importance (lack of previous research on the topic highlighting the gaps, inconsistencies, avoid the comprehensive view.)
	\item Literature (recent studies. last 5 years. )
	\item Knowledge Gap (specific knowledge gaps, inconsistencies, and controversies in the literature. motivate the importance of the study.)
	\item Research Question and Objectives (guide the study units of analysis used in the paper)
	\item Outline Structure (a brief outline of the flow of the entire paper)
\end{itemize}

### 2016-05-08 review.tex
添加了逻辑图，改善文章结构，主要在方法上
add a references
增加文章结构

% !TEX root = Eco-Model.tex
\section{Literature Review} % (fold)
\label{sec:literature_review}

\subsection{Business Mode} % (fold)
\label{sub:business_mode}

% subsection business_mode (end)

\subsection{Cloud Manufacturing} % (fold)
\label{sub:cloud_manufacturing}
% This definition is quite abstract and thus despite its corretness not very useful.
from \textbf{function, resource}, information, process view to depict the cloud manufacturing platform.

@@

\subsection{Manufacturing Ecosystem} % (fold)
\label{sub:manufacturing_ecosystem}
% xx of an ecosystem is a path-dependent, chaotic process, which means that a small difference in starting values can cause great difference to result.

% From a bionomic perspective, organisms and organizations are nodes in networks of relationships. As time passes and evolution proceeds, some nodes are wiped out and new ones crop up, triggering adjustments that ripple across each network. 
\subsubsection{Different Ecosystem Analogies}

\subsubsection{Manufacturing System}
% Constrained by its key relationships, each organism and each organization is held in its niche, pursuing the same goal -- the genetic or technological information it carries.

@@

% Self-organization
% Emergence
% Coevolution
% adaptation

>>>>

% !TEX root = Eco-Model.tex
\section{Literature review} % (fold)
\label{sec:literature_review}
demonstrates that you know the field, justifies the reason for your research, allows you establish your theoretical and needs to be done.
\subsection{Cloud manufacturing} % (fold)
\label{sub:cloud_manufacturing}
% This definition is quite abstract and thus despite its corretness not very useful.
from \textbf{function, resource}, information, process view to depict the cloud manufacturing platform.

In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}

@@

\subsection{Manufacturing ecosystem} % (fold)
\label{sub:manufacturing_ecosystem}
% xx of an ecosystem is a path-dependent, chaotic process, which means that a small difference in starting values can cause great difference to result.

% From a bionomic perspective, organisms and organizations are nodes in networks of relationships. As time passes and evolution proceeds, some nodes are wiped out and new ones crop up, triggering adjustments that ripple across each network. 
\subsubsection{Different ecosystem analogies}

\subsubsection{Manufacturing system}
% Constrained by its key relationships, each organism and each organization is held in its niche, pursuing the same goal -- the genetic or technological information it carries.

@@

% Self-organization
% Emergence
% Coevolution
% adaptation
\subsubsection{E}
